When and Where: Understanding the Patterns of Emergency Service Calls in Toronto

### 2024-09-26 paper/paper.qmd
Changed the code structure
Added test-data.

Moved some data cleaning from paper to cleaning-data.R.

Minor updates: Updated reference, simulate_data

```{r}
#| label: fig-dow
#| fig-cap: Event Type Counts Grouped by Day of the Week
#| echo: false
#| warning: false
#| message: false
data$event_dow <- factor(data$event_dow, 
    levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))

@@

```{r}
#| label: fig-month
#| fig-cap: Event Type Counts Grouped by the Month
#| echo: false
#| warning: false
#| message: false
month_levels <- c("January", "February", "March", "April", "May", "June",
                  "July", "August", "September", "October", "November", "December")

data$event_month <- factor(data$event_month, levels = month_levels)

ggplot(data, aes(x = event_month, fill = event_type)) + 
  geom_bar(position = "dodge") + 
  labs(title = "Event Type Counts Grouped by the Month", 
       x = "Month", 
       y = "Count",
       fill = "Event Type") +
  theme_minimal() +
  coord_flip()
```

@@

>>>>

```{r}
#| label: fig-dow
#| fig-cap: Event Type Counts Grouped by Day of the Week
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-month
#| fig-cap: Event Type Counts Grouped by the Month
#| echo: false
#| warning: false
#| message: false
ggplot(data, aes(x = event_month, fill = event_type)) + 
  geom_bar(position = "dodge") + 
  labs(title = "Event Type Counts Grouped by the Month", 
       x = "Month", 
       y = "Count",
       fill = "Event Type") +
  theme_minimal() +
  coord_flip()
```

@@

- janitor [@janitor]: This package provided helpful tools for data cleaning. Its functionalities greatly enhanced the efficiency and accuracy of our data preparation process.
